### 2022-08-09 paper/main.tex
update paper

\usepackage{amssymb}
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles \left( APA)

\addbibresource{example.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage{import}
\usepackage{float}
\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{pgfplots}
\usepackage{rotating}
\usetikzlibrary{fit}
\usetikzlibrary{calc,patterns,angles,quotes}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

@@

\subject{Computer Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{https://www.uni-kl.de/}{Technische Universität Kaiserslautern}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{https://www.informatik.uni-kl.de/}{German Research Center for Artificial Intelligence}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{https://av.dfki.de/}{Augmented Vision}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://faculty.university.com}{Faculty Name}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

@@

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{https://linkedin.com/in/jingyuan-sha-5b8b43208}{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{https://av.dfki.de/members/stricker/}{\supname}\\
\href{https://av.dfki.de/members/fetzer/}{M. Sc. Torben \textsc{Fetzer}}
 % Supervisor name - remove the \href bracket to remove the link  
\end{flushright}
\end{minipage}\\[3cm]

@@

\groupname\\\deptname\\ % Research group name and department name
\includegraphics{Figures/TUK_LOGO_RGB}\\[2cm] % Research group name and department name

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
We proposed a learning based approach for surface normal estimation based on illuminated calibrated RGB-D image. 
Different with other methods, the approach not only base on geometry information, but also takes the photometric stereo approach into account, which use calibrated illuminated image to further improve the performance. The two types of data gives a superior performance on normal inference task. One of the key points of our approach is, the proposed method require only one light source for each scene capture instead of multiple light positions, which can be very easy to configure in the practice.

Our model is trained on a  gated convolution neural network called (Trip-Net). The gated convolution design is supposed to handle the semi-dense depth map input, which is a common artefact by the depth sensor. Furthermore, a dataset based on 55 point clouds called ``synthetic-50-5“ in created for training. We trained our model on this synthetic dataset then further applied it to real dataset. A qualitative and quantitative evaluation is reported in the end.
\end{abstract}

@@

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
\end{acknowledgements}

@@

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

@@

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\dedicatory{To my fire}

@@

\include{Appendices/AppendixA}
\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

>>>>

\usepackage{amssymb}
%\usepackage[backend=bibte,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles \left( APA)

\usepackage[backend=bibtex,style=numeric]{biblatex}

\addbibresource{example.bib} % The filename of the bibliography
\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage{import}
\usepackage{float}
\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{pgfplots}
\usepackage{rotating}
\usepackage{caption}
\captionsetup[figure]{font=normalsize,labelfont=normalsize}
\captionsetup{justification   = raggedright,
	singlelinecheck = false, width=\linewidth}
\usetikzlibrary{fit}
\usetikzlibrary{calc,patterns,angles,quotes}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

@@

\subject{Computer Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{https://www.uni-kl.de/}{Technische Universität Kaiserslautern}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{https://www.informatik.uni-kl.de/}{Department of Computer Science}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{https://av.dfki.de/}{Augmented Vision}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{https://av.dfki.de/}{Augmented Vision}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

@@

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{https://linkedin.com/in/jingyuan-sha-5b8b43208}{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisors:} \\
\href{https://av.dfki.de/members/stricker/}{\supname}\\
\href{https://av.dfki.de/members/fetzer/}{M. Sc. Torben \textsc{Fetzer}}
 % Supervisor name - remove the \href bracket to remove the link  
\end{flushright}
\end{minipage}\\[3cm]

@@

\groupname\\
\deptname\\ % Research group name and department name
\includegraphics{Figures/TUK_LOGO_RGB}\\[2cm] % Research group name and department name

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
In this work, a learning based approach for surface normal estimation based on illuminiated calibrated RGB-D images is proposed.

This approach extends the geometry based approach by techniques of photometric stereo, which uses calibrated illuminated images for normal estimation. 
The two types of data gives a superior performance on normal inference task. One of the key points of our approach is, the proposed method require only one light source for each scene capture instead of multiple light sources, which can be very easy to configure in the practice.

Our model is trained on a gated convolution neural network (Trip-Net). The gated convolution design is intended to handle the missing pixels in the depth map, which is a common defect of the depth sensor. We also created a dataset of 55 point clouds called \textit{Synthetic-50-5} for training. We trained our model on this synthetic dataset and then applied it to a real dataset. Finally, a qualitative and quantitative evaluation is performed.

\end{abstract}

@@

%\begin{acknowledgements}
%\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
%The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
%\end{acknowledgements}

@@

@@

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------
%
%\dedicatory{To my fire}

@@

\include{Appendices/AppendixA}
\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}
\listoffigures % Prints the list of figures
\listoftables % Prints the list of tables
%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------
